Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-18 Ch1_movement_rates/Ch1_Figures.Rmd
vis table
waaaa updates

```{r}
disp_df %>%
  group_by(., model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

@@

@@

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Shape") +
  theme_bw() -> weib_shape

@@

```
# Table 2 - results

@@

>>>>

# Figure x - average dispersal and dispersion per run

Importance of the outliers here

```{r}
disp_df %>%
  group_by(., model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

disp_df %>%
  group_by(., model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(y = av.disp, x = model)) +
  geom_boxplot() +
  #geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Average dispersal", y = "Dispersal in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersal

@@

# Figure x - seed dispersal kernel parameters
Here we are using the distance of each seed

@@

## Variation 1 - violin plot with 100 out of 1000 of the parameter fits

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(title = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() -> weib_shape

@@

@@

## Variation 2 - violin plot with all 1000 of the parameter fits

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(title = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

## Variation 3 - boxplot with all the fits, 1000

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_boxplot() +
  # geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  #geom_jitter(position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(title = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_boxplot() +
  #geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  #geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

```{r eval=FALSE}

smean.cl.normal(weib.boot.cp$est.shape) -> cp.shape
smean.cl.normal(weib.boot.cp$est.scale) -> cp.scale

smean.cl.normal(weib.boot.pp$est.shape) -> pp.shape
smean.cl.normal(weib.boot.pp$est.scale) -> pp.scale

smean.cl.normal(weib.boot.np$est.shape) -> np.shape
smean.cl.normal(weib.boot.np$est.scale) -> np.scale

cp.df %>% 
  bind_rows(pp.df, np.df) %>% 
  drop_na(., s.id) %>% 
  group_by(model) %>% 
  sample_n(5000) %>% 
  ggplot(., aes(x = disp)) +
  geom_histogram(aes(y = ..density..), fill = "lightgray") +
  stat_function(fun = dweibull, args = list(shape = cp.shape[1], scale = cp.scale[1]), color = "blue") +
  # stat_function(fun = dweibull, args = list(shape = cp.shape[2], scale = cp.scale[2]), color = "blue", lty = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = cp.shape[3], scale = cp.scale[3]), color = "blue", lty = "dashed") +
  stat_function(fun = dweibull, args = list(shape = pp.shape[1], scale = pp.scale[1]), color = "black") +
  # stat_function(fun = dweibull, args = list(shape = pp.shape[2], scale = pp.scale[2]), color = "black", lty = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = pp.shape[3], scale = pp.scale[3]), color = "black", lty = "dashed") +
  stat_function(fun = dweibull, args = list(shape = np.shape[1], scale = np.scale[1]), color = "red") +
  # stat_function(fun = dweibull, args = list(shape = np.shape[2], scale = np.scale[2]), color = "red", lty = "dashed") +
  # stat_function(fun = dweibull, args = list(shape = np.shape[3], scale = np.scale[3]), color = "red", lty = "dashed") +
  theme_bw() +
  geom_vline(aes(xintercept = 500)) +
  coord_cartesian(xlim = c(500, 1700), ylim = c(0, 0.0005))

# Table 2 - results  
Data for each seed, not per run

```{r}
# here::here()
disp_table <- read.csv("Ch1_movement_rates/Figures/table2.csv")

knitr::kable(disp_table)
